Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-03 papers/B1555_EdgeOn/B1555_letter.tex
Minor change in Discussion

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. [here for a precise estimate on substurcture number, mass function, property missing satellite problem]Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from lensed quasars may contain large systematic bias.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous quasars. Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes. [Cant determine on substructure detection] With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. Although radio band provides reliable data on position and fluxe of lensed images, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes and can have impacts on statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk can explain its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
